%-------------------------
% Author: Phong Nguyen
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape NGUYEN LE PHONG} \\ \vspace{1pt}
    \small (+84)98-549-0107 $|$ \href{mailto:phongnguyen.itengineer@gmail.com}{\underline{phongnguyen.itengineer@gmail.com}} $|$ 
    \href{https://github.com/nguyenlephong}{\underline{github.com/nguyenlephong}} $|$ 
    \href{https://www.linkedin.com/in/phong-nguyen-0107/}{\underline{linkedin.com/in/phong-nguyen-0107}}
\end{center}


%-----------ABOUT-----------
\section{SUMMARY}
  \resumeSubHeadingListStart
    \resumeItem{As a front-end software engineer with over five years of experience, I specialize in designing and implementing user-friendly web applications. Proficient in HTML, CSS, JavaScript, and React, my expertise extends to optimizing website performance to accommodate a large user base. My commitment to creating visually appealing and efficient interfaces has led to successful project deliveries across diverse industries.}
    
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, TypeScript, HTML/CSS} \\
     \textbf{Frameworks}{: Spring boot, Node.js, Nextjs, Antdesign} \\
     \textbf{Developer Tools}{: Git, Docker} \\
     \textbf{Libraries}{: React, Redux, React Query, Pupperteer, G2plot}\\
     \textbf{Testing}{: Jest, Cucumber, Testing Library} \\
     \textbf{Other}{: Responsive Design, Cross-Browser Compatibility, SEO}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Math99th}{Remote}
      {Senior Front-end Engineer}{Oct 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Developed a web application for mathematical review using Next.js and Ant Design. Integrated Mathjax for displaying mathematical expressions, ensuring a seamless and visually appealing user experience.}
        \resumeItem{Collaborated with cross-functional teams to align with user needs and optimized application performance. This project showcases my expertise in front-end development and my commitment to delivering innovative solutions.}
      \resumeItemListEnd



    \resumeSubheading
      {PrimeData VN}{Binh Thanh}
      {Senior Front-end Engineer}{Mar. 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Specialized in developing and maintaining intricate UI components and features for their web application.}
        \resumeItem{Leveraging my expertise in code optimization and load time reduction, I have successfully enhanced the application's performance, making it more efficient. Additionally, I play a key role as a mentor, providing technical guidance to junior developers and contributing to the team's growth and success.}
    \resumeItemListEnd
          
   \resumeSubSubheading
    {Full-stack Software Engineer}{July 2020 - Mar 2022}
    \resumeItemListStart
       \resumeItem
         {Designed and developed SDKs and application sets to complement the core application, providing crucial support for development, testing, and marketing teams.}
    \resumeItemListEnd


    \resumeSubheading
      {Splus-Software JSC}{Tan Binh}
      {Java Developer}{Mar 2019 -- July 2020}
      \resumeItemListStart
        \resumeItem{I have completed a wide range of projects, including websites, mobile apps, and internal tools, for both Japanese and American partners.}
        \resumeItem{Working in an outsourcing environment has given me valuable experience in interacting with clients from different cultures and backgrounds, enabling me to develop strong communication and collaboration skills.}
        \resumeItem{Exposure to different projects and deadlines has helped me improve software production processes and time management skills, ensuring timely delivery of high-quality projects.}
        \resumeItem{Using Java, Spring, and React, I have contributed to the development of both front-end and back-end code, adhering to software development best practices and principles such as code quality, testing, and documentation.}
        \resumeItem{Collaborating with a team of developers and project managers has enabled me to showcase my excellent problem-solving skills and attention to detail, ensuring that all projects are completed to the highest standards of quality.}
        \resumeItem{As an onsite representative for Mobivi and Synova companies, I have demonstrated strong communication and collaboration skills with both clients and internal teams, contributing to the growth and success of the company through consistent delivery of high-quality projects and dedication to personal and professional development.}
      \resumeItemListEnd


    \resumeSubheading
      {Mona House}{Remote}
      {Mobile Developer}{Feb 2020 -- May 2020}
      \resumeItemListStart
        \resumeItem{As a mobile app developer, I am highly skilled in React Native development, specializing in creating cross-platform apps with reusable components, smooth animations, and seamless integration with native modules.}
        \resumeItem{Additionally, I possess excellent problem-solving and troubleshooting skills, demonstrating the ability to quickly identify and resolve complex issues using debugging tools, performance profiling, and other advanced techniques.}
        \resumeItem{My adaptability and eagerness to learn new technologies have been key factors in my success, enabling me to quickly grasp and implement new frameworks, programming languages, or tools to complete a project.}
      \resumeItemListEnd

    \resumeSubheading
      {Propman Capital}{District 2}
      {Fresher Front-end Developer}{May 2018 -- Jan 2019}
      \resumeItemListStart
        \resumeItem{As a Fresher Front-end Developer, I've built and maintained our company's main web app, ensuring smooth performance with Redux. I collaborate closely with UX/UI, creating responsive designs for property listing pages. Updated on the latest technologies, contributing to a comprehensive style guide for consistent and maintainable code.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    
      \resumeProjectHeading
          {\textbf{Digital SAT Math} $|$ \emph{React, Next.js, Antdesign, Docker}}{Oct 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Architected the project and implemented all the UI/UX features on the project.}
          \resumeItemListEnd
          
          
      \resumeProjectHeading
          {\textbf{CDP} $|$ \emph{React, Next.js, Antdesign, Redux, WordPress, Docker}}{July 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Architected the project and implemented the majority of the UI/UX features on the project.}
            \resumeItem{Developed ValidatorHOC for every input using ReactHookForm.}
            \resumeItem{Developed SDKs using Service worker, SocketIO, Firebase.}
            \resumeItem{Implemented Data Visualization using G2plot Chart, Apex Chart.}
            \resumeItem{Collaborated with the Design team to ensure UI/UX.}
            \resumeItem{Managed large-scale data, consolidating information from multiple APIs.}
            \resumeItem{Implemented Unit testing, E2E testing, BDD testing.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Vietnam Australia center} $|$ \emph{React, Firebase, Next.js}}{May 2023}
          \resumeItemListStart
            \resumeItem{Took on the responsibility of teaching a Front-end Project course at Vietnam Australia Center.}
          \resumeItemListEnd
          
          
      \resumeProjectHeading
          {\textbf{SmartR.co} $|$ \emph{React, Next.js, Chart.js, Material UI}}{Aug 2022}
          \resumeItemListStart
            \resumeItem{Contributed to a project as a freelancer, focusing on developing a CMS website using Strapi headless CMS.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Bank tool - Mobivi} $|$ \emph{React, Java Spring Boot, MySQL}}{Dec 2019}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application at Mobivi, focusing on ingesting and processing data over 20 Excel files, each containing over 20,000 records.}
            \resumeItem{The application was designed to efficiently handle progressively calculated transactional data from users, ensuring accurate and reliable reporting.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Savyu} $|$ \emph{React Native, React, Node.js}}{May 2019}
          \resumeItemListStart
            \resumeItem{Played a pivotal role in the development of two mobile applications at Synova - one catering to merchants and the other targeting consumers.}
            \resumeItem{Contributed to the creation of a web application empowering administrators to efficiently manage user data.}
            \resumeItem{Demonstrated proficiency in mobile app development, collaborating with cross-functional teams to ensure the successful delivery of intuitive and high-performing applications.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The degree of engineer}{2020}
      {Bachelor's degree in Software Engineering, awarded with a \textbf{very good} classification.}{}
  
    \resumeSubheading
      {Certification in Software Testing}{2019}
      {I was awarded a type-A certificate by GST and invited to join their project.}{}
  
    \resumeSubheading
      {Best Rookie Of The Year}{2019}
      {}{}
  
  \resumeSubHeadingListEnd




%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nong Lam University}{}
      {Bachelor of Information Technology, Minor in Software Engineering}{Sep. 2015 -- Dec 2019}
   
  \resumeSubHeadingListEnd


%-----------REFERENCES-----------
\section{REFERENCES}


\begin{tabular}{lr}
% Referee 1
\begin{minipage}[t]{4in}
\textbf{Mr. NGO VAN KIM KHANH}\\
\textit{Co-founder \& Developer \& CEO, Algae} \\
\textit{SRE \& Cloud/OnPrem Infrastructure, PrimeData VN}\\
\Telefon\ (+84) 907-709-380\\
\Letter\ \href{mailto:khanh.ngo@algae.vn}{khanh.ngo@algae.vn}
\end{minipage}
&

% Referee 2
\begin{minipage}[t]{4in}
\textbf{Mr. NGUYEN NGOC HOAI AN}\\
\textit{Former Chief Technology Officer, PrimeData VN} \\
\\
\Letter\ \href{mailto:me@paulaan.me}{me@paulaan.me}
\\ \href{https://www.linkedin.com/in/paulaan}{linkedin.com/in/paulaan}

\end{minipage}
\\
\\ % Additional newline for spacing.


\end{tabular}

%-------------------------------------------
\end{document}
